Emissions and Perceptions of Climate Change

### 2022-11-18 Code/Draft_GHG_Emissions_&_Perceptions_of_Climate_Change.Rmd
created cleaned up final version

```{r}
fit_add<-decompose(emissions_ts, type='additive')
plot(fit_add)
```
Ya, so I cannot decompose my data. She also did not teach us how to run the test, which is annoying.

@@

```{r}
ggplot(threat, aes(response,Number, fill=Country))+geom_bar(stat = 'identity', position = 'dodge') + xlab("Response to Survey Question")+ ylab("Percent") + theme_bw() + coord_flip()
```
More Americans than Danes think that climate change is a very serious threat, but Danes think it is a somewhat serious threat than Americans. More Americans also think that cliamte change is not a threat at all than Danes. Lets view a pie chart.

@@

>>>>

```{r}
#fit_add<-decompose(emissions_ts, type='additive')
#plot(fit_add)
```
Ya, so I cannot decompose my data. She also did not teach us how to run the test, which is annoying.

@@

```{r}
ggplot(threat, aes(response,Number, fill=Country))+geom_bar(stat = 'identity', position = 'dodge') + xlab("Response to Survey Question")+ ylab("Percent") + theme_bw() + coord_flip()
```
More Americans than Danes think that climate change is a very serious threat, but Danes think it is a somewhat serious threat than Americans. More Americans also think that climate change is not a threat at all than Danes. Lets view a pie chart.

@@

### Viewing the Survey Data
lets view all the survey data in the same graph with a likert graph. 
I need my data in wide format based on response, so I need all four to have the same response. None of them have the same response, and even if I changed the responses they are not in the right order to do. It would be alot of work to do this, so I am going to keep the pie chart method.
```{r}
questions<- survey %>% filter(survey$question=="Ques__Climate_beliefs" | survey$question=="Ques__climate_worry" | survey$question=="Ques__threat_20_years" | survey$question=="Ques__Fossil_moreorless" )

new_q<- c("very much","some", "nuetral", "other", "harms","refuse")
questions_new<- questions %>% filter(survey$question=="Ques__Climate_beliefs") %>% mutate(response=

#survey_wide <– quesitons, id_cols=
```

```{r}
library(likert)
plot(likert(questions), ordered = F, wrap= 60)
```
